\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-02-05 tex/overview.tex
relate interaction graph to Jacobian

% \subsection{Overview}
The dynamical model given in terms of a system of differential equations for any network can be represented in terms of an interaction graph (\ref{fig:biomodelexamples} top row).
For a general system the directed graph $G_X$ that describes the manner in which each of the variables depends upon one another is given by the adjacency matrix $\adj(G_X)$ where $\adj(G_X)_{ij}$ is $1$ for $F_i \hbox{ depends on } x_j$ and $0$ for $F_i \hbox{ does not depend on } x_j$.
%  \begin{displaymath}
%    \adj(G_X)_{ij} = \left\{
%      \begin{array}{ll}
%        1, & F_i \hbox{ depends on } x_j\\
%        0, & F_i \hbox{ does not depend on } x_j
%      \end{array}.
%    \right.
% \end{displaymath}
For large systems, since any given component is only likely to interact with a relatively small proportion of the other components, these matrices may be quite sparse.
We can also associate a linearized interdependency graph $G_A$ given by an adjacency matrix $\adj(G_A)$ to each dynamical system having Jacobian matrix $A$ at some fixed point $\vec{x}^0$ where
 \begin{equation}\label{eq:lininterdepadj}
   \adj(G_A)_{ij} = \left\{
     \begin{array}{lr}
       1, & a_{ij} \neq 0\\
       0, & a_{ij} = 0
     \end{array}.
   \right.
\end{equation}
In general, the graph $G_A$ is a subgraph of $G_X$, however, for nearly all systems, $G_A$ is equivalent to $G_X$. We define the connectivity to be equal to the number of edges in $G_A$, which is equivalent to summing up the number of non-zero entries of $\adj(G_A)$.
These interaction graphs can be viewed as deriving from the combination of system components that accept a given pattern of inputs and produce a given pattern of outputs (\reffigexamplesystemmodules).

>>>>

% \subsection{Overview}
The dynamical model given in terms of a system of differential equations for any network can be represented in terms of a global interaction graph (\ref{fig:biomodelexamples} top row).
For a general system the directed graph $G_X$ that describes the manner in which each of the variables depends upon one another is given by the adjacency matrix $\adj(G_X)$ where $\adj(G_X)_{ij}$ is $1$ for $F_i \hbox{ depends on } x_j$ and $0$ for $F_i \hbox{ does not depend on } x_j$. These two conditions on global system interactions are expressed respectively in terms of elements of the Jacobian matrix as $\frac{\partial F_i}{\partial x_j}(\vec{x}) \neq 0$ for all $\vec{x}$ and $\frac{\partial F_i}{\partial x_j}(\vec{x}) = 0$ for all $\vec{x}$.
%  \begin{displaymath}
%    \adj(G_X)_{ij} = \left\{
%      \begin{array}{ll}
%        1, & F_i \hbox{ depends on } x_j\\
%        0, & F_i \hbox{ does not depend on } x_j
%      \end{array}.
%    \right.
% \end{displaymath}
For large systems, since any given component is only likely to interact with a relatively small proportion of the other components, these matrices may be sparse.
We can also associate a local interaction graph $G_A$ given by an adjacency matrix $\adj(G_A)$ to each dynamical system having Jacobian matrix $A$ at some fixed point $\vec{x}^0$ where
 \begin{equation}\label{eq:lininterdepadj}
   \adj(G_A)_{ij} = \left\{
     \begin{array}{lr}
       1, & a_{ij} \neq 0\\
       0, & a_{ij} = 0
     \end{array}.
   \right.
\end{equation}
In general, the graph $G_A$ is a subgraph of $G_X$, however, for nearly all systems, $G_A$ is equivalent to $G_X$ (\refsupp{}). We define the connectivity to be equal to the number of edges in $G_A$, which is equivalent to summing up the number of non-zero entries of $\adj(G_A)$.
These interaction graphs can be viewed as deriving from the combination of system components that accept a given pattern of inputs and produce a given pattern of outputs (\reffigexamplesystemmodules).
